---
title: "Untitled"
author: "Sanjiv Chemudupati"
date: "4/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(countrycode)
```

```{r}
confirmed_cases_url <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv"
covid_confirmed <- read.csv(confirmed_cases_url,header=TRUE, check.names = FALSE)


head(covid_confirmed)
```
```{r}
asNumeric <- function(x) as.numeric(as.character(x))
factorsNumeric <- function(d) modifyList(d, lapply(d[, sapply(d, is.factor)],asNumeric))
```

```{r}
modify_df <- function(df){
 df <-  df %>% 
  mutate(iso_name = factor(countrycode(`Country/Region`, origin='country.name', destination = 'iso3c', custom_match = c(Kosovo = "KSV", `Diamond Princess` = "DIA", `MS Zaandam` = "MSZ")))) %>% 
  select(-c(`Province/State`, `Country/Region`, Lat, Long)) %>% 
  group_by(iso_name) %>%
  summarise_all(.funs = sum) %>% 
  t() %>% 
  as.data.frame() 

}

```
```{r}
clean_df <- function(df){
  names(df) <- lapply(df[1,], as.character) 
  df <- df[-1,]
  df <- factorsNumeric(df) %>% 
    mutate(Dates = rownames(df))
  }


```


```{r}
covid_confirmed <- modify_df(covid_confirmed) 
covid_confirmed <- clean_df(covid_confirmed)
```



```
```{r}
head(covid_confirmed)
```


```{r}
covid_confirmed$Dates<-paste(covid_confirmed$Dates, "20", sep="") %>% 
  as.factor() %>% 
  strptime(format="%m/%d/%Y") %>% 
  as.Date(format="%Y-%m-%d")
```
```{r}
head(covid_confirmed)
```
```{r}
covid_confirmed$Dates


```


```{r}
countrycode(covid_confirmed$`Country/Region`, origin = 'country.name', destination = 'iso3c', custom_match = c(Kosovo = "KSV", `Diamond Princess` = "DIA", `MS Zaandam` = "MSZ")) 
```
```{r}
y <- countrycode(names(select_if(covid_confirmed, is.numeric)), origin='iso3c', destination = 'country.name', custom_match = c("KSV" = "Kosovo" ,"DIA"= "Diamond Princess", "MSZ"= "MS Zaandam"))
```

```{r}
y
```
```{r}
x <- names(select_if(covid_confirmed, is.numeric))
```

```{r}
names(x) <- y

```
```{r}
names(x)
```

