---
title: "COVID19 Dashboard"
author: "Sanjiv Chemudupati"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    
    navbar:
      - { title: "GitHub", href: "https://github.com/sanjivch/DataScience/tree/master/Machine%20Learning/EDA/Dashboards",  icon: "fa-github" }
      
runtime: shiny
---

```{r setup, include=FALSE}
library(dplyr)
library(stringr)
library(ggplot2)
library(plotly)
library(flexdashboard)
library(countrycode)
library(shiny)
library(leaflet)
library(DT)

```


```{r }
confirmed_cases_url <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv"
covid_confirmed <- read.csv(confirmed_cases_url,header=TRUE, check.names = FALSE)

recovered_cases_url <- 'https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_recovered_global.csv'
covid_recovered <- read.csv(recovered_cases_url,header=TRUE, check.names = FALSE)

deceased_cases_url <- 'https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv'
covid_deceased <- read.csv(deceased_cases_url,header=TRUE, check.names = FALSE)

# Functions to modify  datatype
asNumeric <- function(x) as.numeric(as.character(x))
factorsNumeric <- function(d) modifyList(d, lapply(d[, sapply(d, is.factor)],asNumeric))


modify_df <- function(df){
 df <-  df %>% 
  mutate(iso_name = factor(countrycode(`Country/Region`, origin='country.name', destination = 'iso3c', custom_match = c(Kosovo = "KSV", `Diamond Princess` = "DIA", `MS Zaandam` = "MSZ")))) %>% 
  select(-c(`Province/State`, `Country/Region`, Lat, Long)) %>% 
  group_by(iso_name) %>%
  summarise_all(.funs = sum) %>% 
  t() %>% 
  as.data.frame() 
}

clean_df <- function(df){
  names(df) <- lapply(df[1,], as.character) 
  df <- df[-1,]
  df <- factorsNumeric(df) %>% 
    mutate(Dates = rownames(df)) 
}


# Change the date to required format
covid_confirmed <- covid_confirmed %>% 
  modify_df() %>% 
  clean_df()
covid_confirmed$Dates<-paste(covid_confirmed$Dates, "20", sep="") %>% 
  as.factor() %>% 
  strptime(format="%m/%d/%Y") %>% 
  as.Date(format="%Y-%m-%d")

 covid_recovered <- covid_recovered %>% 
  modify_df() %>% 
  clean_df()
covid_recovered$Dates<-paste(covid_recovered$Dates, "20", sep="") %>% 
  as.factor() %>% 
  strptime(format="%m/%d/%Y") %>% 
  as.Date(format="%Y-%m-%d")

covid_deceased <- covid_deceased %>% 
  modify_df() %>% 
  clean_df()
covid_deceased$Dates<-paste(covid_deceased$Dates, "20", sep="") %>% 
  as.factor() %>% 
  strptime(format="%m/%d/%Y") %>% 
  as.Date(format="%Y-%m-%d")
```
```{r}
covid_india <- read.csv("https://api.covid19india.org/csv/latest/state_wise.csv")
india_coord <- read.csv("https://raw.githubusercontent.com/sanjivch/DataScience/master/Misc/IndianStates_lat_long.csv")

```

```{r}
covid_districts <-  read.csv("https://api.covid19india.org/csv/latest/district_wise.csv")

```



Global
=======================================================================
Column {.sidebar}
-----------------------------------------------------------------------
### Select Country
```{r}
# https://stackoverflow.com/questions/51165189/how-to-efficiently-alias-column-variables-in-the-selectinput-function-in-r-shiny
y <- countrycode(names(select_if(covid_confirmed, is.numeric)), origin='iso3c', destination = 'country.name', custom_match = c("KSV" = "Kosovo" ,"DIA"= "Diamond Princess", "MSZ"= "MS Zaandam"))
x <- names(select_if(covid_confirmed, is.numeric)) 
names(x) <- paste(x, '-', y)
selectInput('country', '', choices = x)

```

Last Updated:
```{r}
renderText(paste(format(covid_confirmed$Dates[nrow(covid_confirmed)],"%Y-%m-%d"), "23:59:59", sep = " "))
```

Row
-----------------------------------------------------------------------


### Confirmed Cases {.value-box data-width=200}

```{r}

confirmed <- reactive({(covid_confirmed[, input$country][nrow(covid_confirmed)])})
renderValueBox({
  valueBox(value = confirmed(), icon = "fa-diagnoses", color = "orange")
})

```

### Recovered Cases {.value-box data-width=200}

```{r}

recovered <- reactive({(covid_recovered[, input$country][nrow(covid_recovered)])})

renderValueBox({
  valueBox(value = recovered(), icon = "fa-user-shield", color = "green")
})
```

### Deceased Cases {.value-box data-width=200}

```{r}
deceased <- reactive({(covid_deceased[, input$country][nrow(covid_deceased)])})


renderValueBox({
  valueBox(value = deceased(), icon = "fa-bed", color = "red")
})
```


### Case Fatality Rate (CFR)  {.value-box data-width=200}

```{r}
pc_mortality <- reactive({round((covid_deceased[, input$country][nrow(covid_deceased)])*100/(covid_confirmed[, input$country][nrow(covid_confirmed)]), digits=2)})


renderValueBox({
  valueBox(value = pc_mortality(), icon = "fa-percent")
})
```


Row 
-----------------------------------------------------------------------------------------
### Daily Cases 

```{r}

renderPlotly({
  
 country_confirmed <- covid_confirmed %>% 
    mutate(confirmed_cases = as.numeric(covid_confirmed[,input$country])) %>% 
    select(Dates, confirmed_cases)
 
  country_recovered <- covid_recovered %>% 
    mutate(recovered_cases = covid_recovered[,input$country]) %>% 
    select(Dates, recovered_cases)
  
  country_deceased <- covid_deceased %>% 
    mutate(deceased_cases = covid_deceased[,input$country]) %>% 
    select(Dates, deceased_cases)
  
  country_data <- full_join(country_confirmed, country_recovered)
  country_data <- full_join(country_data, country_deceased)
  
  covid <- country_data
  
p <- ggplot(data = covid, aes(x = covid$Dates))+
  geom_line(aes(y=covid$confirmed_cases), size = 0.25, color="orange", stat= "identity")+
  geom_point(aes(y=covid$confirmed_cases), size=0.3,color="orange")+
  geom_line(aes(y=covid$recovered_cases), size = 0.25, color="darkgreen", stat= "identity")+
  geom_point(aes(y=covid$recovered_cases),size=0.3,color="darkgreen")+
  geom_line(aes(y=covid$deceased_cases), size = 0.25, color="red", stat="identity")+
  geom_point(aes(y=covid$deceased_cases),size=0.3,color="red")+
  labs(x = "Dates", y = "# of Cases")





ggplotly(p)

print(p)

})


```

Row 
-----------------------------------------------------------------------------------------
### Daily change in Confirmed Cases

```{r}

renderPlotly({
  
  country_confirmed <- covid_confirmed %>% 
    mutate(confirmed_cases = as.numeric(covid_confirmed[,input$country]),
           confirmed_delta = c(0,diff(confirmed_cases, lags =1, differences = 1))) %>% 
    select(Dates, confirmed_cases, confirmed_delta)
 

p <- ggplot(data = country_confirmed, aes(x = Dates, y = confirmed_delta))+
     geom_bar(stat = "identity", fill = "black")+
     labs(x = "Dates", y = "# of cases")


ggplotly(p)

print(p)

})
```
```{r}
states <- covid_india %>% 
          arrange(State) %>% 
          select(State, State_code)
```


India
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------
### Select State/UT
```{r}
y <- states$State
x <- states$State_code
names(x) <- y
selectInput('state', '', choices = x)
```


Row
-----------------------------------------------------------------------

### Total Cases {.value-box }

```{r}
covid_state_total <- covid_india %>% 
               select(State_code, Confirmed)
confirmed1 <- reactive({
  covid_state_total[covid_state_total$State_code == input$state, ][2]
  })

renderValueBox({
  valueBox(value = confirmed1(), icon = "fa-diagnoses", color = "orange")
})

```


### Recovered Cases {.value-box }

```{r}
covid_state_recovered <- covid_india %>% 
               select(State_code, Recovered)
recovered1 <- reactive({
  covid_state_recovered[covid_state_recovered$State_code == input$state, ][2]
  })
renderValueBox({
  valueBox(value = recovered1(), icon = "fa-user-shield", color = "green")
})

```


### Deceased Cases {.value-box }

```{r}
covid_state_deceased <- covid_india %>% 
               select(State_code, Deaths)
deceased1 <- reactive({
  covid_state_deceased[covid_state_deceased$State_code == input$state, ][2]
  })
renderValueBox({
  valueBox(value = deceased1(), icon = "fa-bed", color = "red")
})

```

### Case Fatality Rate (CFR)  {.value-box }

```{r}

covid_state_cfr <- covid_india %>% 
               select(State_code, Confirmed, Deaths)
cfr <- reactive({
  a <- covid_state_cfr[covid_state_cfr$State_code == input$state,][3]
  b <- covid_state_cfr[covid_state_cfr$State_code == input$state,][2]
cfr <- round(a*100/b, digits =2)
  })

renderValueBox({
  valueBox(value = cfr(), icon = "fa-percent")
})
```




Column
-----------------------------------------------------------------------
### Status

```{r}
india_data <- full_join(covid_india, india_coord)
india_data <- india_data[-1,]

india_map <- india_data %>%
            leaflet() %>%
            addTiles() %>%
            addCircles(weight=10,
                       color = "red",
                       radius=~(india_data$Confirmed)*5,
                       popup = paste(india_data$State, 
                               paste("Confirmed",india_data$Confirmed, sep = " : "),
                               paste("Recovered",india_data$Recovered, sep = " : "),
                               paste("Deceased",india_data$Deaths, sep = " : "),
                               paste("Last Updated", india_data$Last_Updated_Time, sep=" : "),
                               sep="<br>"))
india_map


```

### District wise

```{r}
state_name <- reactive({
  if (input$state == 'TT'){
    covid_districts
  } else {
    covid_districts[covid_districts$State_Code == input$state,]
  }
  
})
DT::renderDataTable({
  data <- state_name() %>% 
          select(District, 
                 Confirmed, 
                 Recovered, 
                 Deceased, 
                 Delta_Confirmed, 
                 Delta_Recovered, 
                 Delta_Deceased) 
          
  DT::datatable(data, options = list(
    bPaginate = TRUE,
    scrollX = "200px"
  ))
})


```


Data Source {data-icon="fa-globe"}
=======================================================================

#### Data Source(s)

The data is taken from multiple sources listed below:

1. Global data is from [JHU CSSE](https://github.com/CSSEGISandData/COVID-19)
2. India data is from [COVID19India](https://api.covid19india.org)
3. Latitude and Longitudes for India [LatLong.net](https://www.latlong.net/)

Code for the dashboard is available on my [GitHub/sanjivch](https://github.com/sanjivch/DataScience/tree/master/Machine%20Learning/EDA/Dashboards)


